Final Project Code ALL

### 2022-12-09 Draft_Final_Code.Rmd
More clustering work

```{r}
imdb_clean <- imdb_top_1000 %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = log(Revenue-Budget)) %>%
  select(-...15)

@@

### K-Means Clustering

@@

```{r}
# Select just the bill length and depth variables
imdb_sub <- imdb_clean %>%
    select(Budget, Runtime)

# Run k-means for k = centers = 3
set.seed(253)
kclust_k10 <- kmeans(scale(imdb_sub), centers = 10)

# Display the cluter assignments
kclust_k10$cluster

# Add a variable (kclust_3) to the original dataset 
# containing the cluster assignments
imdb_clean <- imdb_clean %>%
    mutate(kclust_10 = factor(kclust_k10$cluster))
```

```{r}
# Visualize the cluster assignments on the original scatterplot
imdb_clean %>%
  ggplot(aes(x = Budget, y = Runtime, color = kclust_10)) +
    geom_point() + theme_classic()
```

@@

@@

# Display the cluter assignments
kclust_k8$cluster

# Add a variable (kclust_3) to the original dataset 
# containing the cluster assignments
imdb_clean <- imdb_clean %>%
    mutate(kclust_8 = factor(kclust_k8$cluster))
```

@@

*Pick either k = 8 or k = 10 --> there are 7 genres with larger n and 13 total genres. Film noir is fancy way of saying crime drama (ex. Knives Out). One thing to note is a significant number of movies have Genre_2 listed as Family Mystery and Horror (and many have one of the main genres listed as genre 2 as well). What is a good way to summarize both Genre 1 and 2?*

@@

imdb_clean %>%
  count(Genre_2)
```

## Interpreting the Clusters

```{r}
imdb_clean %>%
  group_by(kclust_10) %>%
  summarize(across(c(Gross, Budget), mean))

@@

>>>>

```{r}
imdb_clean <- imdb_top_1000 %>%
  cSplit("Genre", sep = ",", direction = "wide") %>%
  mutate(Gross = log(Revenue-Budget))

@@

# Unsupervised Learning - Clustering

## K-Means Clustering

### Preliminary Visualizations

@@

### Create Clusters

```{r}
imdb_sub <- imdb_clean %>%
    select(Budget, Runtime)

set.seed(253)
```

### Determine Number of Clusters

@@

### Select k = 8 Clusters

@@

kclust_k8$cluster   # Display cluster assignments

imdb_clean <- imdb_clean %>%
    mutate(kclust_8 = factor(kclust_k8$cluster))
```

### Visualize Cluster Assignments

@@

### Interpreting Clusters

#### Exploring Genre Breakdown

@@

imdb_clean %>%
  count(Genre_2)

imdb_clean %>%
  count(New_Genre)
```

```{r}
# Genres vs Cluster

@@

```{r}
imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = Genre_2)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

imdb_clean %>%
  ggplot(aes(x = kclust_8, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()
